---
title: "Missouri Basin Corn and Soy Shocks"
author: "Mandy Liesch"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    source_code: embed
---

```{r setup, include=FALSE}
#load the packages and libraries necessary
library(ggplot2)
library(plotly)
library(knitr)
library(plyr)
library(flexdashboard)
library(tidyverse)
library(ggnewscale)
library(kableExtra)
```

```{r}
#Load the color palettes and files
#Read in the land use files
landUse<-read_csv("LandUse_Shocks.csv")

#Read in the Vegetative Shock File
vegShocks<-read_csv("Vegetative_Shocks.csv")

#Read in the Land Use Color plots
LUColors <- c("UrbanLand"="#C80813FF", "Urban"="#C80813FF", "Tundra"="#71D0F5FF", 
              "Rock/Ice/Desert"="#8A9197FF", "Cropland" = "#FED439FF",
              "HarvCropLand"="#FED439FF", "Harvested Cropland"="#FED439FF", 
              "OtherArableLand" = "#D2AF81FF", "Other Arable Land" = "#D2AF81FF",
              "Pasture"= "#FD8CC1FF", "UnmanagedPasture"="#370335FF", 
              "Unmanaged Pasture"="#370335FF",
              "Grassland" = "#46732EFF", "Forest" = "#075149FF", 
              "Shrubland" = "#F05C3BFF", "otherNotArable"="#8A9197FF")

# Vegetative Based Color Palette
vegCEmissions<-c("#46732EFF")

# Model Based Color Pallete
ModelColors<- c("FAO"="#370335FF", "Houghton" = "#FED439FF", 
                "GCAM" = "#FED439FF", "HWSD"="#1A9993FF", "SG17" = "#197EC0FF",
                "SG20"="#F05C3BFF")

```


```{r}
#Land Use Subsets

#Break up the land leaf columns into subsets 
#(each land leaf has 4 different categories)
new_LU<-landUse %>% 
  separate(LandLeaf, c("LandUse", "Basin", "Water", "Input")) %>%
  #split the scenario column by data
  separate(scenario, into = c('scenario', 'date'), sep = ",") %>%
  #Select everything but date, basin and units
  select(-c("date", "Basin", "Units"))


#Sum together all of the land leaf files by land use type
sum_new_LU<- new_LU %>% 
  group_by(scenario, LandUse) %>% 
  summarise(across(where(is.numeric), sum))

#Reclassify land use types into broader categories
cat_LU<-sum_new_LU %>% 
  mutate(Category = case_when(
  #Cropland category  
  LandUse %in% 
    #Biomass Crops
    c("biomassGrass", "biomassTree",  
    #Fodder Crops
      "FodderGrass", "FodderHerb", 
    #Grain Crops
      "Corn",  "Soybean", "Wheat", "OtherGrain",
    #Oil Crops
      "OilCrop", "Rapeseed", 
    #Other Crops
      "FiberCrop", "MiscCrop", "RootTuber",  "SugarCrop") 
    #Land Use Name
      ~ "HarvCropLand",
    #Other Arable Land
    LandUse == "OtherArableLand" ~"OtherArableLand",
    #Forest categories
    LandUse %in% c("Forest", "UnmanagedForest", "ProtectedUnmanagedForest")
                ~ "Forest",
    #Grassland categories
    LandUse %in% c("Grassland", "ProtectedGrassland") ~ "Grassland", 
    #Pasture category
    LandUse=="Pasture" ~ "Pasture",
    #Unamanged pasture category
    LandUse %in% c("ProtectedUnmanagedPasture", "UnmanagedPasture") 
              ~ "UnmanagedPasture",
    #Shrubland category
    LandUse %in% c("Shrubland", "ProtectedShrubland") ~ "Shrubland",
    #Other categories
    LandUse=="Tundra" ~ "Tundra",
    LandUse=="UrbanLand" ~ "UrbanLand",
    #Default Return Statement
    TRUE~NA_character_
  )
)

#Sum everything up by defined land use category
sum_cat_LU<-cat_LU %>% 
  group_by(scenario, Category) %>% 
  summarise(across(where(is.numeric), sum))

#Create a long dataframe with land use, years, and area 
wide_sum_LU<-sum_cat_LU %>% 
  #Pivot longer creating the year values to area
  pivot_longer(!c(scenario, Category), names_to=c("year"),values_to = "area")%>%
  #convert years into the numeric values
  mutate(year = as.numeric(year)) %>% 
  #Pivot to a wider dataframe utilizing the 3 different shock scenarios
  pivot_wider(names_from = scenario, values_from = c(area)) %>%
  #Calculate the difference in the corn shocks
  mutate(DifCornShock = CORN1BG - BASE) %>%
  #Calculate the difference in the soy shocks
  mutate(DifSoyShock = SOY1BG - BASE) %>%
  #Resort everything by land use category
  group_by(Category) %>%
  #calculate the cumulative land use change in the corn shock 
  mutate(CumSumCornLand = cumsum(DifCornShock)) %>%
  #calculate the cumulative land use changes in the soy shocks
  mutate(CumSumSoyLand = cumsum(DifSoyShock)) %>%
  #Rename the values to work in the ggplotly scenario
     mutate(Category = recode(Category, HarvCropLand = "Harvested Cropland",
         OtherArableLand = "Other Arable Land",
         UnmanagedPasture = "Unmanaged Pasture", 
         UrbanLand = "Urban"
     )
)
```

```{r}
#Vegetative Emission Calculations

#Break up the land leaf columns into subsets 
#(each land leaf has 4 different categories)
new_veg<-vegShocks %>% 
  separate(LandLeaf, c("LandUse", "Basin", "Water", "Input")) %>%
  #separate the scenarios into their correct names
  separate(scenario, into = c('scenario', 'date'), sep = ",") %>%
  #remove the data, basin, and units values from the dataset
  select(-c("date", "Basin", "Units"))


#Sum together all of the land leaf files by land use type
sum_new_veg<- new_veg %>% 
  group_by(scenario, LandUse) %>% 
  summarise(across(where(is.numeric), sum))

#Reclassify land use types into broader categories
cat_veg<-sum_new_veg %>% 
  mutate(Category = case_when(
  #Cropland category  
  LandUse %in% 
    #Biomass Crops
    c("biomassGrass", "biomassTree",  
    #Fodder Crops
      "FodderGrass", "FodderHerb", 
    #Grain Crops
      "Corn",  "Soybean", "Wheat", "OtherGrain",
    #Oil Crops
      "OilCrop", "Rapeseed", 
    #Other Crops
      "FiberCrop", "MiscCrop", "RootTuber",  "SugarCrop") 
    #Land Use Name
      ~ "HarvCropLand",
    #Other Arable Land
    LandUse == "OtherArableLand" ~"OtherArableLand",
    #Forest categories
    LandUse %in% c("Forest", "UnmanagedForest", "ProtectedUnmanagedForest")
                ~ "Forest",
    #Grassland categories
    LandUse %in% c("Grassland", "ProtectedGrassland") ~ "Grassland", 
    #Pasture category
    LandUse=="Pasture" ~ "Pasture",
    #Unamanged pasture category
    LandUse %in% c("ProtectedUnmanagedPasture", "UnmanagedPasture") 
              ~ "UnmanagedPasture",
    #Shrubland category
    LandUse %in% c("Shrubland", "ProtectedShrubland") ~ "Shrubland",
    #Other categories
    LandUse=="Tundra" ~ "Tundra",
    LandUse=="UrbanLand" ~ "UrbanLand",
    #Default Return Statement
    TRUE~NA_character_
  )
)

#Sum everything up by defined land use category
sum_cat_veg<-cat_veg %>% 
  group_by(scenario, Category) %>% 
  summarise(across(where(is.numeric), sum)) %>%
  #only focus on the data to 2060
  select(scenario:'2060')


#Create a long dataframe with land use, years, and area 
wide_sum_veg<-sum_cat_veg  %>% 
  pivot_longer(!c(scenario, Category), names_to=c("year"),values_to = "area")%>%
  #convert years into the numeric values
  mutate(year = as.numeric(year)) %>% 
  #Pivot to a wider dataframe utilizing the 3 different shock scenarios
  pivot_wider(names_from = scenario, values_from = c(area)) %>%
  #Calculate the difference in the corn shocks
  mutate(DifCornShock = CORN1BG - BASE) %>%
  #Calculate the difference in the soy shocks
  mutate(DifSoyShock = SOY1BG - BASE) %>%
  #Resort everything by land use category
  group_by(Category) %>%
  #calculate the cumulative land use change in the corn shock 
  mutate(cumSumCornVeg= cumsum(DifCornShock))%>%
  #calculate the cumulative land use changes in the soy shocks
  mutate(cumSumSoyVeg= cumsum(DifSoyShock)) %>%
      #Rename the categories to fit the ggplotly formatting
     mutate(Category = recode(Category, HarvCropLand = "Harvested Cropland",
         OtherArableLand = "Other Arable Land",
         UnmanagedPasture = "Unmanaged Pasture", 
         UrbanLand = "Urban"
     )
)

#Calculate the total sum of all vegetative sources by year
sum_all_veg <- wide_sum_veg %>%
  group_by(year) %>% 
  summarise(across(where(is.numeric), sum))
```

```{r}
#Soil Data 

#Create a series loop to read in all of the data

#Create a list of all .csv files in the output folder
files <- list.files(path="~/github/GCAMShocks/GCAM_Shocks/Shocks", pattern = "\\values.csv$", 
                    full.names = TRUE)

#Initialize an empty list to store data frames
data_list <- list()

# Loop over each file and read it into a data frame
for (file in files) {
  data <- read.csv(file)
  data_list[[file]] <- data
}

# Combine all data frames into one
combined_shock_soil_data <- bind_rows(data_list)

#Manipulate the data frame for use
new_Soil_Shock_Emiss<- combined_shock_soil_data %>% 
  #Separate the LandLeaf column into 4 categories
  separate(LandLeaf, c("LandUse", "Basin", "Water", "Input")) %>%
  #Separate the scenario column into two categories
  separate(scenario, into = c('scenario', 'date'), sep = ",") %>%
  #Remove the excess columns and select the correct ones
  select(-c("date", "region", "Basin", "Units"))  %>%
  select(Series:'X2060')

#Sum together all of the land leaf files by land use type
sum_new_Soil_Emiss<- new_Soil_Shock_Emiss %>% 
  group_by(Series, scenario, LandUse) %>% 
  summarise(across(where(is.numeric), sum))

#Reclassify land use types into broader categories
cat_Soil_Emiss<-sum_new_Soil_Emiss %>% 
  mutate(Category = case_when(
  #Cropland category  
  LandUse %in% 
    #Biomass Crops
    c("biomassGrass", "biomassTree",  
    #Fodder Crops
      "FodderGrass", "FodderHerb", 
    #Grain Crops
      "Corn",  "Soybean", "Wheat", "OtherGrain",
    #Oil Crops
      "OilCrop", "Rapeseed", 
    #Other Crops
      "FiberCrop", "MiscCrop", "RootTuber",  "SugarCrop") 
    #Land Use Name
      ~ "HarvCropLand",
    #Other Arable Land
    LandUse == "OtherArableLand" ~"OtherArableLand",
    #Forest categories
    LandUse %in% c("Forest", "UnmanagedForest", "ProtectedUnmanagedForest")
                ~ "Forest",
    #Grassland categories
    LandUse %in% c("Grassland", "ProtectedGrassland") ~ "Grassland", 
    #Pasture category
    LandUse=="Pasture" ~ "Pasture",
    #Unamanged pasture category
    LandUse %in% c("ProtectedUnmanagedPasture", "UnmanagedPasture") 
              ~ "UnmanagedPasture",
    #Shrubland category
    LandUse %in% c("Shrubland", "ProtectedShrubland") ~ "Shrubland",
    #Other categories
    LandUse=="Tundra" ~ "Tundra",
    LandUse=="UrbanLand" ~ "UrbanLand",
    #Default Return Statement
    TRUE~NA_character_
  )
)

#Sum everything up by defined land use category
sum_cat_soil_emiss<- cat_Soil_Emiss %>% 
  group_by(Series, scenario, Category) %>% 
  summarise(across(where(is.numeric), sum))

#Create a long dataframe with land use, years, and area 
wide_sum_soil_emiss<- sum_cat_soil_emiss %>% 
  pivot_longer(!c(Series, scenario, Category), 
               names_to=c("year"), values_to = "area") %>%
  #Remove the extra X value from the dataset
  mutate(across(c('year'), substr, 2, nchar(year))) %>%
  #convert years into the numeric values
  mutate(year = as.numeric(year)) %>% 
   #Pivot to a wider dataframe utilizing the 3 different shock scenarios
  pivot_wider(names_from = scenario, values_from = c(area)) %>%
  #calculate the cumulative land use change in the corn shock
  mutate(DifCornShock = CORN1BG - BASE) %>%
  #calculate the cumulative land use change in the soy shock
  mutate(DifSoyShock = SOY1BG - BASE)  %>%
  #Rename the categories to fit the ggplotly formatting
  mutate(Category = recode(Category, HarvCropLand = "Harvested Cropland",
         OtherArableLand = "Other Arable Land",
         UnmanagedPasture = "Unmanaged Pasture", 
         UrbanLand = "Urban")) %>%
  #Rename the GCAM series Houghton
  mutate(Series = recode(Series, GCAM = "Houghton"))

#Calculate the cumulative soil emissions by Series and year
cum_soil_emiss_sums<-wide_sum_soil_emiss %>%
  group_by(Series, year) %>% 
  summarise(across(where(is.numeric), sum)) %>%
  #calculate the cumulative emissions for the corn shock
  mutate(aggDifCorncount = cumsum(DifCornShock)) %>%
  #And for the soy shock
  mutate(aggDifSoycount = cumsum(DifSoyShock))

#Create a new, merged database of soil and vegetative emissions
mergedData<-merge(wide_sum_soil_emiss, wide_sum_veg, 
                  #merge by category and year, keep all values
                  by=c("Category", "year"), all=TRUE) %>%
                  #rename all of the columns after the merge
                  rename( c( "BASE.soil" ="BASE.x", 
                           "BASE.veg" = "BASE.y", 
                           "CORN1BG.soil" =  "CORN1BG.x", 
                           "CORN1BG.veg" = "CORN1BG.y",
                          "SOY1BG.soil" =  "SOY1BG.x", 
                           "SOY1BG.veg" = "SOY1BG.y",
                          "DifCornShock.soil" = "DifCornShock.x", 
                          "DifSoyShock.soil" = "DifSoyShock.x", 
                           "DifCornShock.veg" = "DifCornShock.y", 
                          "DifSoyShock.veg" = "DifSoyShock.y" )) %>%
                #calculate the net totals in the corn shock
                mutate(netDifCornShock = DifCornShock.soil+DifCornShock.veg) %>%
                #And the net totals in the soy shocks
                mutate(netDifSoyShock = DifSoyShock.soil + DifSoyShock.veg)

#Sum everything together by series and year
sum_merged_data <- mergedData %>%
   group_by(Series, year) %>% 
  dplyr::summarise(across(where(is.numeric), sum)) %>%
  #Regroup by series
  group_by(Series) %>%
  #Calculate the cumulative sum of the net difference in the corn shock
  dplyr::mutate(aggNetSumDifCorncount = cumsum(netDifCornShock)) %>%
  #Repeat for the soy shock
  dplyr::mutate(aggNetSumDifSoycount = cumsum(netDifSoyShock)) %>%
  #Calculate the net emissions for the future
  dplyr::mutate(BASENetEmiss = BASE.soil + BASE.veg) %>%
  #regroup
  group_by(Series) %>%
  #filter for data after 2015
  filter(year >2015) %>%
  #Calculate the cumulative net emissions for the baseline into the future
  dplyr::mutate(BASECumNetEmiss = cumsum(BASENetEmiss)) %>%
  #Rename the Houghton data
  mutate(Series = recode(Series, GCAM = "Houghton"))

```

Read Me
=======================================================================

Row
-----------------------------------------------------------------------
### Project Information

The model scenario modeled in this paper represent the reference scenario of the Model Comparison Exercise (EPA, 2023). The scenario was hypothetical and designed solely for the purpose of evaluating and comparing the models utilized in the paper.

Originally, the both vegetative and terrestrial soil carbon values put into GCAM were based on Land type and Biome from Houghton (1999) and King et al. (1997), at a depth of 100 cm. Since the advent of the GCAM model, there have been several new, spatially aware soil models that have been developed. This research is one of the first studies looking at these different soil sources, and how changing the different inputs into the GCAM Land Allocation model changes the overall emissions picture.

There are five different soil carbon sources represented in this research, with interactive display [here](https://agrichick45.github.io/Missouri_Basin_Rasters/soilRastersTogether.html): 

- FAO Glosis dataset 
- Initial Houghton Dataset, scaled down to 30 cm to match the 30 cm input of other data sources
- Harmonized World Soils Database
- SoilGrids 2017 (New default in GCAM after GCAM version 5.1)
- SoilGrids 2020


This is an interactive dashboard set up to visualize the Baseline GCAM model results for the five different soil carbon scenarios, how they impact the baseline emission levels, and the differences in magnitude these initialization impacts mean in the corn and soy shocks. 


### Initial Parameters

```{r}
#Create the data vectors to make the initial parameterization table
Land <- c("Cropland","Forest","Grassland","Pasture","Shrubland", "Urban")
FAO <- c(6.98, 6.20, 6.04, 3.83, 2.24, 6.01)
Houghton <-c(4.65, 8.42, 6.32, 6.04, 3.10, 3.02)
HWSD <- c(6.15, 5.34, 5.30, 4.60, 4.14, 6.13)
SG17 <- c(7.76, 9.92, 7.64, 6.58, 5.50, 5.80)
SG20 <- c(6.28, 4.97, 5.89, 4.51, 3.56, 4.00)

#combined the vectors together to create a data frame
df <- data.frame(Land, FAO, Houghton, HWSD, SG17, SG20) 

#Format the table
df %>%
  #if the values are numeric, we only want 3 digits
  mutate_if(is.numeric, format, digits=3) %>%
  #align the columns in the center
  kbl(align = "c") %>% 
  #custominze the html values for the output
  kable_material(c("striped", "hover", full_width = F))

```

Row
-----------------------------------------------------------------------
### Dashboard Introduction

There are 5 tabs, plus this initial Read Me. The **Baseline Scenarios**, which have the actual numbers associated with the reference scenarios for each of the simulations. These results are located in *The Net and cumulative Emissions* pane. 

The *Soil Emission Plots* show the input based differences in the corn and soy shocks for each of these 5 soil models above the baseline model. The *Vegetative Plots*, and *Land Use Plots* have the same values in all five soil model scenarios, and these tabs show how the values of the corn and soy shocks relative to the baseline scenarios changes. 

The initialization parameters for each model are listed in the table here. Each plot in this dashboard is clickable, and lines can be toggled on and off, zoomed in on, and panned. 

In the Missouri River Basin, the biggest land use changes in the future timesteps involve the transition from unmanaged pasture to cropland. This difference of the initial parameters: Unmanaged Pasture - Cropland. In all of these results, the order of the results match the order of this change, largest to smallest in this order. The magnitude and oscillations differ in size, but the order does not.

- Houghton: 1.39 kg/m^2
- SG17: -1.18 kg/m^2
- HWSD: -1.55 kg/m^2 
- SG20: -1.77 kg/m^2
- FAO GLOSIS: -3.15 kg/m^2


### Tab Description
**Definitions**

*NET Emissions:* Soil + Vegetative Carbon added together for the current year

*CUMULATIVE Emissions:* 2015 as year 1, to 2060, adding the current years net emissions to the sum of the previous years 


**Future Baseline Scenarios:** 

- Baseline Land Use Change - Projected Area (Mha) 
- Baseline Soil and Vegetative Emissions - Annual Mt Emissions of the Vegetative Carbon and soil carbon for all 5 models
- Net Baseline Emissions - for all 5 models
- Net Cumulative Baseline Emissions - Cumulative emissions from 2015 to 2060 for the reference scenario

**Net and Cumulative Emissions:**

- Net Baseline Emissions - for all 5 models
- Total Net Corn and Net Soy Shock Emissions Over Baseline
- Total Cumulative Net Corn and Soy Shock Emissions Over Baseline

**Soil Emission Plots:** 

- Total Corn and Soy Shock Emissions Over Baseline
- Soil Cumulative Corn and Soy Shock Emissions Over Baseline
- Key Corn and Soy Land Use Emission Changes Over Baseline in the FAO model


**Vegetative Plots:** 

- Total Corn and Soy Shock Vegetative Emission Change Over Baseline 
- Total Cumulative Corn and Soy Shock Vegetative Emission Change Over Baseline 
- Key Corn and Soy Land Use Emission Changes Over Baseline

**Land Use Plots:** 

- Baseline Land Use Change (Line Plot)
- Corn and Soy Shock Land Use Change Over Baseline by Key Land Use Type
- Cumulative Corn and Soy Shock Land Use Change Over Baseline by Key Land Use Type
 

Future Baseline Scenarios
=======================================================================

Row
-----------------------------------------------------------------------
### Baseline Land Use Change

```{r}
#Create the baseline land use change plot
LandUseAreaFuture.plt<- ggplot(wide_sum_LU %>%
                                 #Remove the non dynamic categories
                                 filter(Category !=c("Tundra")) %>%
                                 filter(Category !=c("Urban")) %>%
                                 #Remove the data from 2015
                                 filter(year >2010), 
                                 #graph the baseline data by land use category
                                 aes(x=year, y=BASE, fill=Category)) + 
  #Use a stacked bar plot
  geom_bar(position="stack", stat="identity") +
  #add the labels
  labs(fill = "Land Use (Mha)", x='Year', y='Mha') + 
  #set the legend to be on one line
  #guides(fill = guide_legend(nrow = 1)) +
  #Use the custom designed color pallette and set names and labels
  scale_fill_manual(values=LUColors)

ggplotly(LandUseAreaFuture.plt)



```

### Baseline Soil and Vegetative Emissions

```{r}
#Calculate the future emissions plots
futureEmissions.plt<-ggplot(data=sum_merged_data %>%
                              filter(year >2015), aes(x=year))+
  #Add a line plot for the soil emissions by series
  geom_line(aes(y=BASE.soil,
       group=Series, color=Series), lwd=2) +
      #Add the custom color manual and labels
      scale_color_manual(values=c(ModelColors)) +

  #Add a line plot for the vegetative emissions
  geom_line(aes(y=BASE.veg, color="Vegetation"), lwd=2) +

  #Add the title
  #ggtitle("Future Emissions") +
  #Add the theme elements
  #theme(plot.title = element_text(hjust = 0.5)) +
  #Add the labels
  labs( x='Year', y='Total Emissions (Mt)') 

ggplotly(futureEmissions.plt)

```

Row
-----------------------------------------------------------------------
### Net Baseline Emissions
```{r}
#Calculate the net emissions plots by series
futNetEmissions.plt<-ggplot(data=sum_merged_data %>%
                              #filter to years greater than 2015
                              filter(year >2015), 
                            aes(x=year, y=BASENetEmiss, group=Series))+
  geom_line(aes(color=Series), lwd=2) +
      #Add the custom color manual and labels
      scale_color_manual(values=c(ModelColors, name = "Emissions"), 
                      labels = c("FAO Glosis", "Houghton", "HWSD", 
                                 "SoilGrids 2017", "SoilGrids 2020")) +
  #Add the title
  #ggtitle("Future Net Emissions") +
  #Add the theme elements
  #theme(plot.title = element_text(hjust = 0.5)) +
  #Add the labels
  labs( x='Year', y='Total Emissions (Mt)') 
  
ggplotly(futNetEmissions.plt)
```

### Net Cumulative Baseline Emissions
``` {r}
futCumNetEmissions.plt<-ggplot(data=sum_merged_data %>%
                              filter(year >2015), 
                            aes(x=year, y=BASECumNetEmiss, group=Series))+
  geom_line(aes(color=Series), lwd=2) +
      #Add the custom color manual and labels
      scale_color_manual(values=c(ModelColors, name = "Emissions"), 
                      labels = c("FAO Glosis", "Houghton", "HWSD", 
                                 "SoilGrids 2017", "SoilGrids 2020")) +
  #Add the title
  #ggtitle("Future Net Emissions") +
  #Add the theme elements
  #theme(plot.title = element_text(hjust = 0.5)) +
  #Add the labels
  labs( x='Year', y='Total Emissions (Mt)') 
  
ggplotly(futCumNetEmissions.plt)

```



Net and Cumulative Emissions 
=======================================================================

Row
-----------------------------------------------------------------------
### Graphical Interpretations

### Total Net Corn and Soy Shock Emissions Over Baseline

```{r}



net_emiss_CSSS_Models.plt<-ggplot(data= sum_merged_data %>%
                                    filter(year > 2015)) + 
  geom_line(aes(x=year, y=netDifCornShock, color=Series, linetype="Corn"), size=2) +
    geom_line(aes(x=year, y=netDifSoyShock, color=Series, linetype="Soy"), size=2) +
  #add a title
  #ggtitle("Total Net Corn Shock Emissions Over Baseline") +
  #add labels
  labs( x='Year', y='Emissions (Mt)', linetype="Shock Type") + 
  #use the custom color pallette
  scale_color_manual(values=ModelColors)

ggplotly(net_emiss_CSSS_Models.plt)
```


Row
-----------------------------------------------------------------------
### Net Baseline Emissions 

```{r}
#Calculate the net emissions plots by series
futNetEmissions.plt<-ggplot(data=sum_merged_data %>%
                              #filter to years greater than 2015
                              filter(year >2015), 
                            aes(x=year, y=BASENetEmiss, group=Series))+
  geom_line(aes(color=Series), lwd=2) +
      #Add the custom color manual and labels
      scale_color_manual(values=c(ModelColors, name = "Emissions"), 
                      labels = c("FAO Glosis", "Houghton", "HWSD", 
                                 "SoilGrids 2017", "SoilGrids 2020")) +
  #Add the title
  #ggtitle("Future Net Emissions") +
  #Add the theme elements
  #theme(plot.title = element_text(hjust = 0.5)) +
  #Add the labels
  labs( x='Year', y='Total Emissions (Mt)') 
  
ggplotly(futNetEmissions.plt)
```

### Total Cumulative Net Corn and Soy Shock Emissions Over Baseline

```{r}
cum_net_emiss_CSSS_Models.plt<-ggplot(data= sum_merged_data %>%
                                    filter(year > 2015))+
  geom_line(aes(x=year, y=aggNetSumDifCorncount, color=Series, linetype="Corn"), size=2) +
  geom_line(aes(x=year, y=aggNetSumDifSoycount, color=Series, linetype="Soy"), size=2) +
  #add a title
  #ggtitle("Total Cumulative Net Corn Shock Emissions Over Baseline") +
  #add labels
  labs( x='Year', y='Emissions (Mt)', linetype="Shock Scenarios") +
  #use the custom color pallette
  scale_color_manual(values=ModelColors)

ggplotly(cum_net_emiss_CSSS_Models.plt)
```





Soil Emission Plots
=======================================================================

Row
-----------------------------------------------------------------------
###

### Total Corn and Soy Shock Emissions Over Baseline

```{r}

  
cum_soil_emiss_sums_CSSS_Models.plt<-ggplot(data= cum_soil_emiss_sums %>%
                                    filter(year > 2015))+
  geom_line(aes(x=year, y=DifCornShock, color=Series, linetype="Corn"), size=2) +
  geom_line(aes(x=year, y=DifSoyShock, color=Series, linetype="Soy"), size=2) +
  #add a title
  #ggtitle("Total Corn Shock Emissions Over Baseline") +
  #add labels
  labs( x='Year', y='Emissions (Mt)', linetype="Shock Type") +
  #use the custom color pallette
  scale_color_manual(values=ModelColors)
# Use hollow circles
ggplotly(cum_soil_emiss_sums_CSSS_Models.plt)
```


Row
-----------------------------------------------------------------------
### Soil Carbon Emissions by Key Land Use Type in the FAO Model
 
```{r}
tot_soil_emiss_sums_LU_Models.plt<-ggplot(data= mergedData %>%
                                   filter(Series == "FAO") %>%
                                    filter(year > 2015) %>%
                                   filter(Category != "Pasture") %>%
                                   filter(Category !=  "Shrubland") %>%
                                   filter(Category != "Tundra") %>%
                                   filter(Category != "Urban"))+
                              
  geom_line(aes(x=year, y=DifCornShock.soil, color=Category, linetype="Corn"), size=2) +
  geom_line(aes(x=year, y=DifSoyShock.soil, color=Category, linetype="Soy"), size=2) +
  #add a title
  #ggtitle("Soil Cumulative Corn Shock Emissions Over Baseline") +
  #add labels
  labs( x='Year', y='Emissions (Mt)', linetype="Shock Type") +
  #use the custom color pallette
  scale_color_manual(values=LUColors)



# Add a loess smoothed fit curve with confidence region
ggplotly(tot_soil_emiss_sums_LU_Models.plt)
```

### Soil Cumulative Corn and Soy Shock Emissions Over Baseline

```{r}
tot_cum_soil_emiss_sums_CSSS_Models.plt<-ggplot(data= cum_soil_emiss_sums %>%
                                    filter(year > 2015))+
  geom_line(aes(x=year, y=aggDifCorncount, color=Series, linetype="Corn"), size=2) +
  geom_line(aes(x=year, y=aggDifSoycount, color=Series, linetype="Soy"), size=2) +
  #add a title
  #ggtitle("Soil Cumulative Corn Shock Emissions Over Baseline") +
  #add labels
  labs( x='Year', y='Emissions (Mt)', linetype="Shock Type") +
  #use the custom color pallette
  scale_color_manual(values=ModelColors)



# Add a loess smoothed fit curve with confidence region
ggplotly(tot_cum_soil_emiss_sums_CSSS_Models.plt)
```


Vegetative Plots
=======================================================================

Row
-----------------------------------------------------------------------
### 

### Corn and Soy Shock Vegetative Emission Change Over Baseline

```{r}

#Create a spaghetti plot of land use area using area by category
CornSoyShockVegLines.plt<-ggplot(data= sum_all_veg %>%
                                 filter(year >2015))+
  geom_line(aes(x=year, y=DifCornShock, linetype="Corn"), size=2) +
  geom_line(aes(x=year, y=DifSoyShock, linetype="Soy"), size=2) +
  #add a title
  #ggtitle("Corn Shock Vegetative Emission Change Over Baseline by Land Use Type") +
  #add labels
  labs( x='Year', y='Vegetative Emissions (Mt)', linetype = "Shock Values") +
  #use the custom color pallette
  scale_color_manual(values=vegCEmissions)

ggplotly(CornSoyShockVegLines.plt)
```



Row
-----------------------------------------------------------------------
### Corn and Soy Shock Vegetation Emissions Over Baseline by Key Land Use Type

```{r}

#Create a spaghetti plot of land use area using area by category
CornSoyShockLUVegLines.plt<-ggplot(data=wide_sum_veg %>%
                                 filter(year >2015) %>%
                                   filter(Category != "Pasture") %>%
                                   filter(Category !=  "Shrubland") %>%
                                   filter(Category != "Tundra") %>%
                                   filter(Category != "Urban"))+
  geom_line(aes(x=year, y=DifCornShock, color=Category, linetype="Corn"), size=2) +
  geom_line(aes(x=year, y=DifSoyShock, color=Category, linetype="Soy"), size=2) +
  #add a title
  #ggtitle("Corn Shock Vegetative Emission Change Over Baseline by Land Use Type") +
  #add labels
  labs( x='Year', y='Vegetative Emissions (Mt)', linetype = "Shock Values") +
  #use the custom color pallette
  scale_color_manual(values=LUColors)

ggplotly(CornSoyShockLUVegLines.plt)
```

### Cumulative Corn and Soy Shock Vegetative Emission Change Over Baseline

```{r}
#Create a spaghetti plot of land use area using area by category
cumCornSoyShockVegLines.plt<-ggplot(data= sum_all_veg %>%
                                 filter(year >2015))+
  geom_line(aes(x=year, y=cumSumCornVeg, linetype="Corn"), size=2) +
  geom_line(aes(x=year, y=cumSumSoyVeg, linetype="Soy"), size=2) +
  #add a title
  #ggtitle("Corn Shock Vegetative Emission Change Over Baseline by Land Use Type") +
  #add labels
  labs( x='Year', y='Vegetative Emissions (Mt)', linetype="Shock Values") +
  #use the custom color pallette
  scale_color_manual(values=vegCEmissions)

ggplotly(cumCornSoyShockVegLines.plt)                        
```




Land Use Plots
=======================================================================

Row
-----------------------------------------------------------------------
### Interpretaions

1) This is the line plot representation of the stacked bar chart measuring baseline land use changes in the reference scenario. This plot is here to provide the overall framework of changes. The biggest changes occur in Unmanaged Pasture (loss of 63.02 Mha over 45 years), with a majority of land gained from converstion to cropland (gain of 69.36 Mha). Other gains were from reforestation (5.11 Mha) and increases in managed pasture (2.56 Mha), and other losses were other arable land (8.48), Grassland (3.93 Mha), and Shrubland (1.63 Mha). 

2) Soy shocks show more land use changes than corn shocks. At the peak of the shocks in 2030, there is an additional 0.43 Mha of Harvested Cropland over the baseline and an additional loss of 0.34 Mha from Unmanaged Pasture. The differences from the baseline in other arable land (0.04 Mha) and grassland (0.02) are much smaller. As the time continued, the rate of change relative to the baseline between the corn and soy shocks drops to 0.25 Mha for Harvested cropland, and 0.19 Mha for Unmanaged Pasture. 

### 2) Corn and Soy Shock Land Use Change Over Baseline by Key Land Use Type

```{r}
#Create a spaghetti plot of land use area using area by category
CornSoyShockLandUseLines.plt<-ggplot(data= wide_sum_LU %>%
                                 filter(Category !=c("Tundra")) %>%
                                 filter(Category !=c("Urban")) %>%
                                 filter(Category !=c("Pasture"))  %>%
                                 filter(Category !=c("Shrubland")) %>%
                                 filter(year >2015))+
  geom_line(aes(x=year, y=DifCornShock, color=Category, linetype="Corn"), size=2) +
  geom_line(aes(x=year, y=DifSoyShock, color=Category, linetype="Soy"), size=2) +
  #add a title
  #ggtitle("Corn Shock Land Use Change Over Baseline by Land Use Type") +
  #add labels
  labs( x='Year', y='Land Area (Mha)', linetype="Shock Type") +
  #use the custom color pallette
  scale_color_manual(values=LUColors, name = "Land Use")

ggplotly(CornSoyShockLandUseLines.plt)

```



Row
-----------------------------------------------------------------------

### 1) Baseline Land Use Change (Line Plot)

```{r}
#Create the baseline land use change plot
LandUseAreaLineFuture.plt<- ggplot(wide_sum_LU %>%
                                 #Remove the non dynamic categories
                                 filter(Category !=c("Tundra")) %>%
                                 filter(Category !=c("Urban")) %>%
                                 #Remove the data from 2015
                                 filter(year >2010), 
                                 #graph the baseline data by land use category
                                 aes(x=year, y=BASE, color=Category)) + 
  #Use a stacked bar plot
  geom_line(size=2)  +
  #add the labels
  labs(fill = "Land Use (Mha)", x='Year', y='Mha') + 
  #set the legend to be on one line
  #guides(fill = guide_legend(nrow = 1)) +
  #Use the custom designed color pallette and set names and labels
  scale_color_manual(values=LUColors)

ggplotly(LandUseAreaLineFuture.plt)



```

### 3) Cumulative Corn and Soy Shock Land Use Change Over Baseline by  Key Land Use Type

```{r}
#Create a spaghetti plot of land use area using area by category
CumCornSoyShockLandUseLines.plt<-ggplot(data= wide_sum_LU %>%
                                 filter(Category !=c("Tundra")) %>%
                                 filter(Category !=c("Urban")) %>%
                                 filter(Category !=c("Pasture"))  %>%
                                 filter(Category !=c("Shrubland")) %>%
                                 filter(year >2015))+ 
                        
  geom_line(aes(x=year, y=CumSumCornLand, color=Category, linetype="Corn"), size=2) +
  geom_line(aes(x=year, y=CumSumSoyLand, color=Category, linetype="Soy"), size=2) +
  scale_color_manual(values=LUColors) +
  #add a title
  #ggtitle("Corn Shock Land Use Change Over Baseline by Land Use Type") +
  #add labels
  labs( x='Year', y='Land Area (Mha)')

ggplotly(CumCornSoyShockLandUseLines.plt)
```

